|

### 2022-07-31 paper_comparison/paper_comparison/paper_comparison.Rmd
update example plot for power overview

```{r eval = FALSE}
polynomials %>%
  group_by(lineup_id) %>%
  summarise(dd = first(abs(effect_size - exp(2)))) %>%
  arrange(dd)
```

```{r power-overview, fig.height=7.5, fig.cap="Power overview. \\label{fig:power-overview}"}
conv_test_plot() %>%
  add_wrong_BP_conv_test_plot_layers() %>%
  add_wrong_WS_conv_test_plot_layers() %>%
  add_visual_test_plot_layers() +
  geom_vline(xintercept = 0) + 
  geom_vline(xintercept = 2) +
  geom_vline(xintercept = 4) +
  geom_vline(xintercept = 6) -> base_plot

VI_MODEL$plot_lineup(polynomials_lineup$lineup_314$data,
                     size = 0.1,
                     stroke = 0.2,
                     remove_grid_line = TRUE,
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) +
  ggtitle(bquote(log[e](E) == 0~", F-test p-value" == .(format(filter(polynomials, lineup_id == 314)$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(polynomials, lineup_id == 314)$p_value[1], digits = 3)))) -> bottom_plot_1

VI_MODEL$plot_lineup(polynomials_lineup$lineup_415$data,
                     size = 0.1,
                     stroke = 0.2,
                     remove_grid_line = TRUE,
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) +
  ggtitle(bquote(log[e](E) == 2~","~"F-test p-value" == .(format(filter(polynomials, lineup_id == 415)$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(polynomials, lineup_id == 415)$p_value[1], digits = 3)))) -> bottom_plot_2

VI_MODEL$plot_lineup(polynomials_lineup$lineup_494$data,
                     size = 0.1,
                     stroke = 0.2,
                     remove_grid_line = TRUE,
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) +
  ggtitle(bquote(log[e](E) == 4~","~"F-test p-value" == .(format(filter(polynomials, lineup_id == 494)$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(polynomials, lineup_id == 494)$p_value[1], digits = 3)))) -> bottom_plot_3

VI_MODEL$plot_lineup(polynomials_lineup$lineup_101$data,
                     size = 0.1,
                     stroke = 0.2,
                     remove_grid_line = TRUE,
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) +
  ggtitle(bquote(log[e](E) == 6~","~"F-test p-value" == .(format(filter(polynomials, lineup_id == 101)$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(polynomials, lineup_id == 101)$p_value[1], digits = 3)))) -> bottom_plot_4

>>>>

```{r eval = FALSE}
polynomials %>%
  group_by(lineup_id) %>%
  summarise(dd = first(abs(log(effect_size) - 5)), p_value = first(p_value)) %>%
  arrange(dd)

polynomials %>%
  ggplot() +
  geom_point(aes(prop_detect, p_value < 0.06))

bottom_plot_2
```

```{r power-overview, fig.height=7.5, fig.cap="Power overview. \\label{fig:power-overview}"}
conv_test_plot() %>%
  add_wrong_BP_conv_test_plot_layers() %>%
  add_wrong_WS_conv_test_plot_layers() %>%
  add_visual_test_plot_layers() +
  geom_vline(xintercept = 2, linetype = 2) + 
  geom_vline(xintercept = 3, linetype = 2) +
  geom_vline(xintercept = 4, linetype = 2) +
  geom_vline(xintercept = 5, linetype = 2) -> base_plot

# VI_MODEL$plot_lineup(polynomials_lineup$lineup_314$data,
#                      size = 0.1,
#                      stroke = 0.2,
#                      remove_grid_line = TRUE,
#                      theme = theme_light(base_size = 5),
#                      remove_axis = TRUE) +
#   ggtitle(bquote(log[e](E) == 0~", F-test p-value" == .(format(filter(polynomials, lineup_id == 314)$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(polynomials, lineup_id == 314)$p_value[1], digits = 3)))) -> bottom_plot_1

VI_MODEL$plot_lineup(polynomials_lineup$lineup_415$data,
                     size = 0.1,
                     stroke = 0.2,
                     remove_grid_line = TRUE,
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) +
  ggtitle(bquote(log[e](E) == 2~","~"F-test p-value" == .(format(filter(polynomials, lineup_id == 415)$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(polynomials, lineup_id == 415)$p_value[1], digits = 3)))) -> bottom_plot_1

VI_MODEL$plot_lineup(polynomials_lineup$lineup_364$data,
                     size = 0.1,
                     stroke = 0.2,
                     remove_grid_line = TRUE,
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) +
  ggtitle(bquote(log[e](E) == 3~", F-test p-value" == .(format(filter(polynomials, lineup_id == 364)$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(polynomials, lineup_id == 364)$p_value[1], digits = 3)))) -> bottom_plot_2

VI_MODEL$plot_lineup(polynomials_lineup$lineup_574$data,
                     size = 0.1,
                     stroke = 0.2,
                     remove_grid_line = TRUE,
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) +
  ggtitle(bquote(log[e](E) == 4~","~"F-test p-value" == .(format(filter(polynomials, lineup_id == 574)$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(polynomials, lineup_id == 574)$p_value[1], digits = 3)))) -> bottom_plot_3

VI_MODEL$plot_lineup(polynomials_lineup$lineup_179$data,
                     size = 0.1,
                     stroke = 0.2,
                     remove_grid_line = TRUE,
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) +
  ggtitle(bquote(log[e](E) == 5~","~"F-test p-value" == .(format(filter(polynomials, lineup_id == 179)$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(polynomials, lineup_id == 179)$p_value[1], digits = 3)))) -> bottom_plot_4
